Supplementary Material for: A Rough Guide to Pre-processing High-Frequency Animal Tracking Data

### 2021-02-17 _03_smoothing_tracks.Rmd
edits to figure 3

```{r}
# smooth the data over four K values
list_of_smooths <- lapply(c(3, 5, 11, 21), function(K) {
  data_copy <- copy(data_errors)

@@

```{r}
fwrite(list_of_smooths[[3]], file = "data/data_smooth.csv")
```

@@

```{r echo=FALSE}
# prepare data to plot
# make list of data to plot
figure_median_smooth <-
  ggplot() +
  geom_path(
    data = data_errors,
    aes(x, y,
      group = offset
    ),
    col = "grey60",
    size = 0.1
  ) +
  geom_point(
    data = data_errors[offset == 0, ],
    aes(x, y),
    col = pal[3],
    size = 0.2
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    lwd = 0.5
  ) +
  geom_path(
    data = data_plot,
    aes(x, y,
      group = window_size,
      col = window_size
    ),
    show.legend = F,
    lwd = 0.3
  ) +
  coord_equal(
    expand = F,
    ylim = c(0.6, 0.85),
    xlim = c(NA, 2.3),
    ratio = 1.75
  ) +
  annotate(
    geom = "text",
    x = c(0.75, seq(1.1, 2, length.out = 4)),
    y = 0.82,
    label = sprintf("(%s)", letters[seq(5)]),
    fontface = "bold"
  ) +
  scale_colour_distiller(
    palette = "BuPu", direction = 1,
    values = c(-2, 1)
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  )

>>>>

```{r}
# smooth the data over four K values
list_of_smooths <- lapply(c(5, 11, 21, 101), function(K) {
  data_copy <- copy(data_errors)

@@

```{r}
fwrite(list_of_smooths[[2]], file = "data/data_smooth.csv")
```

@@

```{r echo=FALSE}
# prepare data to plot
# make list of data to plot
figure_median_smooth <-
  ggplot() +
  geom_path(
    data = data_errors,
    aes(x, y,
      group = offset
    ),
    col = "grey60",
    size = 0.1
  ) +
  geom_point(
    data = data_errors[offset == 0, ],
    aes(x, y),
    col = pal[3],
    size = 0.2
  ) +
  geom_path(
    data = data,
    aes(x, y),
    col = "grey20",
    lwd = 0.5
  ) +
  geom_path(
    data = data_plot,
    aes(x, y,
      group = window_size,
      col = factor(window_size)
    ),
    show.legend = F,
    lwd = 0.35
  ) +
  coord_equal(
    expand = F,
    ylim = c(0.6, 0.83),
    xlim = c(NA, 2.3),
    ratio = 1.75
  ) +
  annotate(
    geom = "text",
    x = c(0.75, seq(1.1, 2, length.out = 4)),
    y = 0.81,
    label = sprintf("(%s)", letters[seq(5)]),
    fontface = "bold"
  ) +
  scale_colour_manual(
    values = c(colorspace::sequential_hcl(3, l = 40, palette = "PuBu",
                                          rev = T), "sienna")
  ) +
  ggthemes::theme_few() +
  theme(
    axis.text = element_blank(),
    axis.title = element_blank()
  )
